---
title: "a no-frills flipbook"
author: "Gina Reynolds, Dec 2019"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [lucy-fonts, ninjutsu]
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


---

# preamble

The "YMAL", a preamble that defines settings for your Rmarkdown document, looks like this: 

```r
---
title: "a no-frills flipbook"
author: "Gina Reynolds, Dec 2019"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [ninjutsu]                 
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```

Ninjutsu gives you the side-by-side.

---

In Xaringan, slide breaks are indicated by three dashes `---` at the beginning of a line, with nothing following (not even white space).

"Next slide"

---

# Set up

Okay. Let's load the the `flipbookr` package and set some helpful knitr options. We also adjust the theme for xaringan.
In a real project, you might set the code chunk option `include` to `FALSE`.

```{r setup, message = F,  warning = F}
# you can install flipbooker as follows from github
# devtools::install_github("EvaMaeRey::flipbookr")
library(flipbookr)

# setting chunk options that will apply to the rest of the book
knitr::opts_chunk$set(fig.width = 6, 
                      message = F, 
                      warning = F, 
                      comment = "", 
                      cache = T)
```


---

`r flipbookr::apply_reveal("basic_plot")`



```{r basic_plot, echo = F, eval = F, fig.height=5}
library(tidyverse)
cars %>%             # the data  #REVEAL
  filter(speed > 4) %>%  # subset
  ggplot() +              # pipe to ggplot
  aes(x = speed) +
  aes(y = dist) +
  # Describing what follows
  geom_point(alpha = .5,
             size = 3) + #REVEAL
  aes(color = dist > 50) 
```
 

 


```{css, eval = TRUE, echo = F}
.remark-code{line-height: 1.5; font-size: 80%}
```
